Compiling refinement types to dependent types

### 2020-07-23 tex/paper.tex
Add TWF-Base case

    We do not mention the premises of the translated rule.
    By \cref{lma:non_dep_pair_typing}
    $(\hat B, \unitc \equiv \unitc)$ has type $\star$ in $\nonterm{GC}$
    if $\hat B$ and $\unitc \equiv \unitc$ are well-typed in $\nonterm{GC}$,
    which, in turn, is easily checked.
    Thus, there exists a derivation of $\nonterm{GC} \vdash (\hat B, \unitc \equiv \unitc) : *$,
    and it is effectively constructible~--- we just omit it for brevity.
  \item \textsc{TWF-Arr}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\\\
                   \nonterm G \vdash \nonterm{ts}_1 \\
                   \nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2}
                  {\nonterm G \vdash (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2}
          \longmapsto
        \inferrule{\Tranty(\nonterm G \vdash \nonterm{ts}_1) \\
                   \Tranty(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2)}
                  {\nonterm{GC} \vdash \Pi x : \nonterm{tc}_1. \nonterm{tc}_2 : \star}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok),                                         \\
                   &\nonterm{tc}_1 = \tranty(\nonterm G \vdash \nonterm{ts}_1),                         \\
                   &\nonterm{tc}_2 = \tranty(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2).
    \end{align*}

>>>>

    We do not mention the premises of the translated rule.
    By \cref{lma:non_dep_pair_typing}
    $(\hat B, \unitc \equiv \unitc)$ has type $\star$ in $\nonterm{GC}$
    if $\hat B$ and $\unitc \equiv \unitc$ are well-typed in $\nonterm{GC}$,
    which, in turn, is easily checked.
    Thus, there exists a derivation of $\nonterm{GC} \vdash (\hat B, \unitc \equiv \unitc) : *$,
    and it is effectively constructible~--- we just omit it for brevity.
  \item \textsc{TWF-Base}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\\\
                   \nonterm G ' \vdash \nonterm{es}_1 : \{ v_2 : B' | \nonterm{r}_1 \} \\\\
                   \nonterm G ' \vdash \nonterm{es}_2 : \{ v_2 : B' | \nonterm{r}_2 \} \\\\
                   \gterm x \fresh}
                  {\nonterm G \vdash \{ v : B | \nonterm{es}_1 = \nonterm{es}_2 \}}
          \longmapsto
        \inferrule{\Tranterm(\nonterm G ' \vdash \nonterm{es}_1 : \{ v_2 : B' | \nonterm{r}_1 \}) \\\\
                   \Tranterm(\nonterm G ' \vdash \nonterm{es}_2 : \{ v_2 : B' | \nonterm{r}_2 \}) \\\\
                   \gterm x \fresh \\\\
                   \cdots}
                  {\nonterm{GC} \vdash (v : \hat B \dast \lambda v : \hat B. \nonterm{ec}_1 \equiv \nonterm{ec}_2) : \star}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok), \\
                   &\nonterm G ' = \nonterm G , v : \{ v_1 : B | \top \}, \\
                   &\nonterm{ec}_i =
                     \tranterm(\nonterm G , x : \{ v_1 : B | \top \} \vdash \nonterm{es}_i : \{ v_2 : B' | \nonterm{r}_i \}).
    \end{align*}

    To see that this is well-defined, first note that
    that $\hat B$ has type $\star$ by assumption on $\hat B$.
    Then, $\nonterm{ec}_1$ and $\nonterm{ec}_2$ are well-typed in the translated context $\nonterm G'$ according to the premises,
    and this context coincides with the one used to type check $\lambda v : \hat B. \nonterm{ec}_1 \equiv \nonterm{ec}_2$.
    Hence both components of the dependent pair are well-typed, so by \cref{lma:dep_pair_typing} the dependent pair itself has type $\star$.

    Just as in the previous case, the extra derivations and premises corresponding to the considerations above
    are omitted and denoted by $\cdots$.
  \item \textsc{TWF-Arr}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\\\
                   \nonterm G \vdash \nonterm{ts}_1 \\
                   \nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2}
                  {\nonterm G \vdash (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2}
          \longmapsto
        \inferrule{\Tranty(\nonterm G \vdash \nonterm{ts}_1) \\
                   \Tranty(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2)}
                  {\nonterm{GC} \vdash \Pi x : \nonterm{tc}_1. \nonterm{tc}_2 : \star}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok),                                         \\
                   &\nonterm{tc}_1 = \tranty(\nonterm G \vdash \nonterm{ts}_1),                         \\
                   &\nonterm{tc}_2 = \tranty(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2).
    \end{align*}
